Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-05-13 reports/manuscript.Rmd
Finish refactor of manuscript

keywords          : "keywords"
wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"

@@

```{r, load-targets}
targets::tar_load(c(
    "manuscript_info", "combined_bib", "reviews_tables",
    "plots", "studies_results", "studies_converted",
    "comparison_plots", "combined_effects", "combined_bib"
),
store = here::here("_targets")
)
```

@@

```{r eduoutcomes}
edu_effect <-
    combined_effects %>%
    filter(outcome_category == "education" & use_effect)

edu_certain <-
    combined_effects %>%
    filter(outcome_category == "education" & certainty == "meets criteria")

n_edu_effect <-
    edu_effect %>%
    nrow()

n_edu_certain <-
    edu_certain %>%
    nrow()

n_edu_noindiv <-
    edu_effect %>%
    filter(source == "reported") %>%
    nrow()

n_edu_samplesize <-
    edu_effect %>%
    filter(source == "reanalysis" & n < 1000) %>%
    nrow()

n_edu_faileggers <-
    edu_effect %>%
    filter(source == "reanalysis" & n > 1000 &
        (eggers_p < 0.05 | is.na(eggers_p))) %>%
    nrow()

n_edu_failtest <-
    edu_effect %>%
    filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>%
    nrow()

n_edu_unique <- n_distinct(edu_certain$covidence_review_id)

edu_summary <-
    studies_converted %>%
    filter(effect_size_id %in% edu_certain$effect_size_id) %>%
    group_by(study_author, study_year, study_first_page_number) %>%
    slice_max(study_n, with_ties = FALSE) %>%
    ungroup() %>%
    summarise(
        studies_n = n(),
        total_n = sum(study_n)
    )
```

There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
Effects not meeting one or more of these standards are presented in Supplementary File 4.
The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.

@@

```{r educertain}
n_edu_p999 <- edu_certain %>%
    filter(reanalysis_p.value < 0.001) %>%
    nrow()
n_edu_p95 <- edu_certain %>%
    filter(reanalysis_p.value < 0.05) %>%
    nrow() - n_edu_p999

n_edu_i2 <- edu_certain %>%
    filter(i2 > 50) %>%
    nrow()
```

As shown in Figure \@ref(fig:eduplot), most of the credible results (`r n_edu_p999` of `r n_edu_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining `r xfun::numbers_to_words(n_edu_p95)` associations were significant at the 95% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
Most effects showed high levels of heterogeneity (`r n_edu_i2` of `r n_edu_certain` with $I^2 > 50\%$).

@@

```{r healthoutcome}
health_effect <-
    combined_effects %>%
    filter(outcome_category != "education" & use_effect)

health_certain <-
    combined_effects %>%
    filter(outcome_category != "education" & certainty == "meets criteria")

n_health_effect <-
    health_effect %>%
    nrow()

n_health_certain <-
    health_certain %>%
    nrow()

n_health_noindiv <-
    health_effect %>%
    filter(source == "reported") %>%
    nrow()

n_health_samplesize <-
    health_effect %>%
    filter(source == "reanalysis" & n < 1000) %>%
    nrow()

n_health_faileggers <-
    health_effect %>%
    filter(source == "reanalysis" & n > 1000 &
        (eggers_p < 0.05 | is.na(eggers_p))) %>%
    nrow()

n_health_failtest <-
    health_effect %>%
    filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>%
    nrow()

n_health_unique <- n_distinct(health_certain$covidence_review_id)

health_summary <-
    studies_converted %>%
    filter(effect_size_id %in% health_certain$effect_size_id) %>%
    group_by(study_author, study_year, study_first_page_number) %>%
    slice_max(study_n, with_ties = FALSE) %>%
    ungroup() %>%
    summarise(
        studies_n = n(),
        total_n = sum(study_n)
    )
```

We identified `r n_health_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed `r n_health_noindiv` effects that did not provide individual study-level data, `r n_health_samplesize` effects with samples < 1,000, and `r n_health_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 5.
The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
These `r n_health_certain` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.

@@

```{r healthcertain}
n_health_p999 <- health_certain %>%
    filter(reanalysis_p.value < 0.001) %>%
    nrow()
n_health_p95 <- health_certain %>%
    filter(reanalysis_p.value < 0.05) %>%
    nrow() - n_health_p999

n_health_i2 <- health_certain %>%
    filter(i2 > 50) %>%
    nrow()
n_health_r2 <- health_certain %>%
    filter(abs(r) < 0.2) %>%
    nrow()
```

Across the health outcomes, most (`r n_health_p999` of `r n_health_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
Most of the effect sizes (`r n_health_r2`/`r n_health_certain`) had an absolute value of $r < 0.2$.

>>>>

keywords          : "keywords"

@@

```{r, load-targets}
targets::tar_load(c(
    "manuscript_info", "combined_bib", "reviews_tables", "combined_bib", "plots"
),
store = here::here("_targets")
)
```

@@

There were `r manuscript_info$edu$n_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
Effects not meeting one or more of these standards are presented in Supplementary File 4.
The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
These `r manuscript_info$edu$n_certain` effects came from `r manuscript_info$edu$n_unique` meta-analytic reviews analysing data from `r manuscript_info$edu$summary$studies_n` empirical studies with `r format(manuscript_info$edu$summary$total_n, big.mark=",")` individual participants.

@@

As shown in Figure \@ref(fig:eduplot), most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).

@@

We identified `r manuscript_info$health$n_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed `r manuscript_info$health$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$health$n_samplesize` effects with samples < 1,000, and `r manuscript_info$health$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 5.
The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
These `r manuscript_info$health$n_certain` effects came from `r manuscript_info$health$n_unique` meta-analytic reviews analysing data from `r manuscript_info$health$summary$studies_n` empirical studies with `r format(manuscript_info$health$summary$total_n, big.mark=",")` individual participants.

@@

Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
